---
title: "Quiz 1 Week 1 R Markdown file"
author: "Me"
date: "4/5/2020"
output:
  pdf_document: default
  word_document: default
---
## Reading in the data
### Reading in the data method 1

```{r}
getwd()
```

```{r}
data <- read.csv("hw1_data.csv")
```

### Reading in the data method 2
```{r}
dat <- download.file('https://d396qusza40orc.cloudfront.net/rprog/data/quiz1_data.zip', destfile ="quizdat.zip")
dat <- unzip("quizdat.zip")
dat <- read.csv("hw1_data.csv")

```
## In the dataset provided for this Quiz, what are the column names of the dataset?
### MEethod 1
```{r}
colnames(data)
```
### Method 2
```{r}
head(data)
```
### Method 3
```{r}
names(dat)
```
##  Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

### Method 1
```{r}
dat[1:2, ]
```
### Method 2
```{r}
dat[152:153, ]
```

### Method 3
```{r}
tail(data, 2)
```

## How many observations (i.e. rows) are in this data frame? 

```{r}
nrow(data)
```
## Question 15 What is the value of Ozone in the 47th row? 

### Method 1

```
data[47, ]

###
```{r}
dat$Ozone[47]
```


## How many missing values are in the Ozone column of this data frame?

### Method 1
```{r}
sum(is.na(dat$Ozone))
```
### Method 2
```{r}
sub <- subset(data, is.na(Ozone))
nrow(sub)
```
### Method 3
#### To calculate as an example how many missing values there are in total
```{r}
length(which(is.na((data))))
```
#### To calculate only for Ozone
```
datana <- subset(dat, is.na(Ozone))
nrow(datana)

## What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

### Method 1
```
datanotna <- subset(dat, !is.na(Ozone))
apply(datanotna, 2, mean)

### Method 2
```
mean(dat$Ozone, na.rm = TRUE)
### Method 3
```{r}
sub = subset(data, !is.na(Ozone), select = Ozone)
apply(sub, 2, mean)
```

## Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?

### Method 1
```{r}
sub <- subset(data, Ozone > 31 & Temp >90, select = Solar.R)
apply(sub, 2, mean)
```
### Method 2
```{r}
mean(dat[which(dat$Ozone >31 & dat$Temp > 90),]$Solar.R)
```
### Method 3 
```{r}
datasub <- subset(dat, dat$Ozone > 31 & dat$Temp >90, select = Solar.R)
apply(datasub, 2, mean)
```
## What is the mean of “Temp” when “Month” is equal to 6?
### Method 1
```
mean(dat[which(dat$Month == 6), ]$Temp)
```
### Method 2
```
sub = subset(dat, Month == 6, select = Temp)
apply(sub, 2, mean)
```
### Method 3
```
datasub <- subset(data, data$Month == 6, select = Temp)
apply(datasub, 2 , mean)
```

## What was the maximum ozone value in the month of May (i.e. Month = 5)
### Method 1
```
datasub <- subset(data, !is.na(Ozone) & data$Month ==5, select = Ozone)
apply(datasub, 2, max)
```
### Method 2
```
sub <- subset(data, Month == 5 & !is.na(Ozone), select = Ozone       )
apply(sub, 2, max)
```